---
title: "report_figures_juliette"
author: "Juliette Verstaen"
date: "2/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE, message=FALSE}
library(ggplot2)
library(here)
library(plotly)
library(tidyverse)
library(gganimate)
library(ggrepel)
library(ggridges)
library(ggpubr)
library(gridExtra)
library(grid)
```

#importing the dataset only looking at 2015-2065
```{r}
#res<-read.csv(here::here("Scenarios", "PatchModel_size.csv"))%>%
 # filter(Year <= 2065 & Adjusted== "IUU_0")

#bmsy<- expression(paste(B/B[MSY]))
#fmsy <- expression(paste(F/F[MSY]))

```

```{r}

res<- read_csv("/GitHub/2019GP/Juliette/PatchModel_size.csv")%>%
  filter(Year <= 2065)

res$Implementation_year [res$Implementation_year== "0"] <- "BAU"
res$Implementation_year <- factor(res$Implementation_year, levels = c("Initial", "BAU", "2015", "2020", "2025", "2030"))
res$Reserve_size <- factor(res$Reserve_size, levels = c("BAU", "5%", "20%", "30%", "40%", "50%"))
  
bmsy<- expression(paste(B/B[MSY]))
fmsy <- expression(paste(F/F[MSY]))
```

##New Final Graphs!!!

A. Reserve Size 5%
Bubbles:
- Implement 2015. BAU bubble; raw data (2015/5/0/0); IUU (2015/5/40/0); Legalize (2015/5/40/40)
- Implement 2020. raw data (2020/5/0/0); IUU (2020/5/40/0); Legalize (2020/5/40/40)
- Implement 2030. raw data (2030/5/0/0); IUU (2030/5/40/0); Legalize (2030/5/40/40)

```{r}

circle_A<- res%>%
  filter(Reserve_size == "5%" | Reserve_size== "BAU") %>%
  group_by(Adjusted, Implementation_year)%>%
  summarize(Biomass_est=sum(Biomass_est), 
            Catch_est=sum(Catch_est), 
            PV_est=sum(PV_est)) %>%
  mutate(Biomass_est=Biomass_est/1000)%>%
  mutate(PV_est=PV_est/1000000) %>%
  filter(Adjusted == "IUU_0" | Adjusted == "IUU_40" | Adjusted == "IUU_40_legal")%>%
  filter(Implementation_year != "2025")
circle$Implementation_year<- as.factor(circle$Implementation_year)

```

```{r}

circle_graph_A <- ggplot(circle_A) +
  geom_point(aes(x=Biomass_est, y=PV_est, size=Catch_est, color = Implementation_year, label=Adjusted), shape = 21)+
  guides(size= "none")+
  scale_size_continuous(range = c(10, 35)) +
  xlim(600, 1400)+
  ylim(40, 175)+
  theme_classic()+
  xlab("Biomass (1000 MT)") +
  ylab("Profits (Millions US$)")+
  annotate(geom="text", x=700, y=77, label="Unadjusted Catch Data",color="black", size= 3) +
  annotate(geom="text", x=1000, y=117, label="Accounting for IUU",color="black", size= 3)+
  annotate(geom="text", x=1200, y=175, label="Perfect Enforcement",color="black", size= 3)+
  ggtitle("Marine Reserve Network 5% of Project Area")+
  theme(legend.title = element_blank())
  

circle_graph_A

#ggsave("circles_A.jpg", width=7, height=5, dpi=300)

```


B. Reserve Size 30%
Bubbles:
-  Implement 2015. BAU bubble; raw data (2015/30/0/0); IUU (2015/30/40/0); Legalize (2015/30/40/40)
-  Implement 2020. raw data (2020/30/0/0); IUU (2020/30/40/0); Legalize (2020/30/40/40)
- Implement 2030. raw data (2030/30/0/0); IUU (2030/30/40/0); Legalize (2030/30/40/40)

```{r}

circle_B<- res%>%
  filter(Reserve_size == "30%" | Reserve_size== "BAU") %>%
  group_by(Adjusted, Implementation_year)%>%
  summarize(Biomass_est=sum(Biomass_est), 
            Catch_est=sum(Catch_est), 
            PV_est=sum(PV_est)) %>%
  mutate(Biomass_est=Biomass_est/1000)%>%
  mutate(PV_est=PV_est/1000000) %>%
  filter(Adjusted == "IUU_0" | Adjusted == "IUU_40" | Adjusted == "IUU_40_legal")%>%
  filter(Implementation_year != "2025")
circle$Implementation_year<- as.factor(circle$Implementation_year)

```

```{r}

circle_graph_B <- ggplot(circle_B) +
  geom_point(aes(x=Biomass_est, y=PV_est, size=Catch_est, color = Implementation_year), shape = 21)+
  guides(size= "none")+
 scale_size_continuous(range = c(10, 35)) +
 xlim(600, 2200)+
 ylim(60, 172)+
  theme_classic()+
  xlab("Biomass (1000 MT)") +
  ylab("Profits (Millions US$)")+
annotate(geom="text", x=677.4844, y=62, label="1",color="black", size= 3) +
  annotate(geom="text", x=1343.4884, y=105, label="1",color="black", size= 3)+
  annotate(geom="text", x=1287.4819, y=82, label="1",color="black", size= 3)+
  annotate(geom="text", x=1165, y=73, label="1",color="black", size= 3)+
  annotate(geom="text", x=964.6503, y=91.5, label="2",color="black", size= 3)+
  annotate(geom="text", x=1909.5335, y=143, label="2",color="black", size= 3)+
  annotate(geom="text", x=1831.8947, y=120, label="2",color="black", size= 3)+
  annotate(geom="text", x=1646.1131, y=105, label="2",color="black", size= 3)+
  annotate(geom="text", x=1920, y=160, label="3",color="black", size= 3)+
  ggtitle("Marine Reserve Network 30% of Project Area") +
  theme(legend.title = element_blank())
  
  
circle_graph_B

#ggsave("circles_B.jpg", width=7, height=5, dpi=300)

```


```{r}

circle_graph_B.1 <- ggplot(circle_B) +
  geom_point(aes(x=Biomass_est, y=PV_est, size=Catch_est, color = Implementation_year), shape = 21)+
  guides(size= "none")+
 scale_size_continuous(range = c(10, 35)) +
 xlim(600, 2200)+
 ylim(60, 172)+
  theme_classic()+
  xlab("Biomass (1000 MT)") +
  ylab("Profits (Millions US$)")+
annotate(geom="text", x=710, y=62, label="Unadjusted Catch Data",color="black", size= 3) +
  annotate(geom="text", x=1287.4819, y=82, label="Unadjusted Catch Data",color="black", size= 3)+
  annotate(geom="text", x=964.6503, y=91.5, label="Accounting for IUU",color="black", size= 3)+
  annotate(geom="text", x=1831.8947, y=120, label="Accounting for IUU",color="black", size= 3)+
  annotate(geom="text", x=1920, y=160, label="Perfect Enforcement",color="black", size= 3)+
  ggtitle("Marine Reserve Network 30% of Project Area")+
  theme(legend.title = element_blank())
  
  
circle_graph_B.1

#ggsave("circles_B.1.jpg", width=7, height=5, dpi=300)

```


C. Reserve Size 50%
Bubbles:
- Implement 2015. BAU bubble; raw data (2015/50/0/0); IUU (2015/50/40/0); Legalize (2015/50/40/40)
- Implement 2020. raw data (2020/50/0/0); IUU (2020/50/40/0); Legalize (2020/50/40/40)
-  Implement 2030. raw data (2030/50/0/0); IUU (2030/50/40/0); Legalize (2030/50/40/40)

```{r}

circle_C<- res%>%
  filter(Reserve_size == "50%" | Reserve_size== "BAU") %>%
  group_by(Adjusted, Implementation_year)%>%
  summarize(Biomass_est=sum(Biomass_est), 
            Catch_est=sum(Catch_est), 
            PV_est=sum(PV_est)) %>%
  mutate(Biomass_est=Biomass_est/1000)%>%
  mutate(PV_est=PV_est/1000000) %>%
  filter(Adjusted == "IUU_0" | Adjusted == "IUU_40" | Adjusted == "IUU_40_legal")%>%
  filter(Implementation_year != "2025")
circle$Implementation_year<- as.factor(circle$Implementation_year)

```

```{r}

circle_graph_C <- ggplot(circle_C) +
  geom_point(aes(x=Biomass_est, y=PV_est, size=Catch_est, color = Implementation_year), shape = 21)+
  guides(size= "none")+
 scale_size_continuous(range = c(10, 35)) +
 xlim(600, 2450)+
 ylim(50, 165)+
  theme_classic()+
  xlab("Biomass (1000 MT)") +
  ylab("Profits (Millions US$)")+
annotate(geom="text", x=730, y=68, label="Unadjusted Catch Data",color="black", size= 3) +
  annotate(geom="text", x=1500, y=65, label="Unadjusted Catch Data",color="black", size= 3) +
  annotate(geom="text", x=964.6503, y=102, label="Accounting for IUU",color="black", size= 3) +
  annotate(geom="text", x=2116.1685, y=92, label="Accounting for IUU",color="black", size= 3) +
  annotate(geom="text", x=2300, y=118, label="Perfect Enforcement",color="black", size= 3) +
  annotate(geom="text", x=2071.9284, y=160, label="Perfect Enforcement",color="black", size= 3) +

  ggtitle("Marine Reserve Network 50% of Project Area")+
  theme(legend.title = element_blank())
  

circle_graph_C

#ggsave("circles_C.jpg", width=7, height=5, dpi=300)

```








OLD

Summing up cummulative biomass and pv of all genuses OA

```{r}

circle<- res%>%
  filter(Reserve_size == "5%" | Reserve_size== "BAU") %>%
  group_by(Adjusted, Implementation_year)%>%
  summarize(Biomass_est=sum(Biomass_est), 
            Catch_est=sum(Catch_est), 
            PV_est=sum(PV_est)) %>%
  mutate(Biomass_est=Biomass_est/1000)%>%
  mutate(PV_est=PV_est/1000000)
circle$Implementation_year<- as.factor(circle$Implementation_year)

#bio_pv_2035 <- res%>%
#  filter(Reserve_size == "5%")%>%
#  filter(Year <= "2035")%>%
#  group_by(Implementation_year, Adjusted)%>%
#  summarize(Biomass_est=sum(Biomass_est), 
#            Catch_est=sum(Catch_est), 
#            PV_est=sum(PV_est))
#bio_pv_2035$Implementation_year<- as.factor(bio_pv_2035$Implementation_year)

```


```{r}

circle_graph <- ggplot(circle) +
  geom_point(aes(x= Biomass_est, y= PV_est, size=Catch_est, color = Implementation_year), shape = 21)+
  guides(size= "none")+
  scale_size_continuous(range = c(15, 30)) +
  #annotate(geom="text", x=1256.866, y=361.405921, label="318K MT",
           #   color="black") +
  #annotate(geom="text", x=1253.392, y=364.691491, label="319K MT",
           #   color="black")+
  #annotate(geom="text", x=1247.927, y=369.812271, label="321K MT",
          #    color="black")+
  #annotate(geom="text", x=1240.207, y=375.365648, label="324K MT",
          #    color="black")+
  #annotate(geom="text", x=1188.948, y=377.850277, label="332K MT",
          #    color="black")+
  #xlim(1170, 1270)+
  #ylim(360, 380)+
  theme_classic()+
  xlab("Biomass (1000 MT)") +
  ylab("Profits (Millions US$)")
  

circle_graph

#ggsave("agg_circles.jpg", width=7, height=5, dpi=300)

```

Summing up cummulative biomass and pv of all genuses F= FMSY
Every column ends up being the same regardless of implementation date

side notw for seleni: looked at data, BAU (Implementation_year=0) only for the 5% implementation option; would be super useful to compare graphs if it was for all reserve sizes
```{r}


#fmsy<- read.csv(here::here("Scenarios", "PatchModel_FMSY.csv"))%>%
  #filter(Adjusted=="IUU_0")


#circle_fmsy<- fmsy%>%
#  filter(Reserve_size == "5%") %>%
#  group_by(Implementation_year, Adjusted) %>%
#  summarize(Biomass_est=sum(Biomass_est), 
#            Catch_est=sum(Catch_est), 
#            PV_est=sum(PV_est))

#circle_fmsy$Implementation_year<- as.factor(circle_fmsy$Implementation_year)

```

Circle graphs with 40% protected

```{r}

circle_40<- res%>%
  filter(Reserve_size == "40%" | Reserve_size =="BAU") %>%
  group_by(Implementation_year, Adjusted)%>%
  summarize(Biomass_est=sum(Biomass_est), 
            Catch_est=sum(Catch_est), 
            PV_est=sum(PV_est))
circle_40$Implementation_year<- as.factor(circle_40$Implementation_year)


circle_40_graph <- ggplot(circle_40) +
  geom_point(aes(x= Biomass_est, y= PV_est, size=Catch_est, color = Implementation_year), shape = 21)+
  scale_size_continuous(range = c(11, 25)) +
  theme_classic()+
  ggtitle("Aggregate Regional Affects 40% Protected")
  

circle_40_graph

#ggsave("agg_circles_40.jpg", width=7, height=5, dpi=300)

```


Circle graphs with 20% protected

```{r}

circle_20<- res%>%
  filter(Reserve_size == "20%" | Reserve_size == "BAU") %>%
  group_by(Implementation_year, Adjusted)%>%
  summarize(Biomass_est=sum(Biomass_est), 
            Catch_est=sum(Catch_est), 
            PV_est=sum(PV_est))
circle_20$Implementation_year<- as.factor(circle_20$Implementation_year)


circle_20_graph <- ggplot(circle_20) +
  geom_point(aes(x= Biomass_est, y= PV_est, size=Catch_est, color = Implementation_year), shape = 21)+
#  scale_size_continuous(range = c(11, 25)) +
  theme_classic()+
  ggtitle("Aggregate Regional Affects 20% Protected")
  

circle_20_graph

#ggsave("agg_circles_30.jpg", width=7, height=5, dpi=300)

```



Graphs seperated out by implmentation date (too similar to do all on one graph)
y axis= year; y-axis = biomass; size= catch, color = money made
OA
**These are interesting because you can see the delayed effect of fishing pressure (with catch and increase profits) after the biomass spike and how the fishing pressure contines to be the same even though biomass decreases and then they bascially crash the fishery

```{r}

library(dplyr)

linepoint <- res %>%
    filter(Reserve_size == "5%" | Reserve_size == "BAU") %>%
  group_by(Year, Implementation_year, Adjusted)%>%
  summarize(Biomass_est=sum(Biomass_est), 
            Catch_est=sum(Catch_est), 
            PV_est=sum(PV_est)) %>%
  mutate(Biomass_est=Biomass_est/1000)
linepoint$Implementation_year<- as.factor(linepoint$Implementation_year)
  

#Genus_ts <- read_csv("data/Genus_ts.csv")

historic <- Genus_ts %>%
  filter(Adjusted == "IUU_0") %>%
  filter(year>="2005") %>%
  filter(year != "2015") %>%
  group_by(year) %>%
  summarize(catch=sum(catch),
            b=sum(b))%>%
  mutate(b=b/1000)

colnames(historic) <- c("Year", "Catch_est", "Biomass_est")

initial <-linepoint %>%
  filter(Implementation_year== "0") 
initial <- full_join(historic, initial, by=c("Year", "Biomass_est", "Catch_est"))

second <- filter(linepoint, Implementation_year == "2015")
second <- full_join(historic, second, by=c("Year", "Biomass_est", "Catch_est"))

third <- filter(linepoint, Implementation_year == "2020")
third <- full_join(historic, third, by=c("Year", "Biomass_est", "Catch_est"))

fourth <- filter(linepoint, Implementation_year == "2025")
fourth <- full_join(historic, fourth, by=c("Year", "Biomass_est", "Catch_est"))

fifth <- filter(linepoint, Implementation_year == "2030")
fifth <- full_join(historic, fifth, by=c("Year", "Biomass_est", "Catch_est"))

initial_graph <- ggplot(initial,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est, show.legend= FALSE))+
  geom_point()+
  ggtitle("BAU")+
  ylab("Biomass 1000 (MT)")+
  theme_classic()

second_graph <- ggplot(second,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est, show.legend= FALSE))+
  geom_point()+
  ggtitle("2015")+
  ylab("Biomass 1000 (MT)")+
  theme_classic()

third_graph <- ggplot(third,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est, show.legend= FALSE))+
  geom_point()+
  ggtitle("2020")+
  ylab("Biomass 1000 (MT)")+
  theme_classic()

fourth_graph <- ggplot(fourth,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est, show.legend= FALSE))+
  geom_point()+
  ggtitle("2025")+
  ylab("Biomass 1000 (MT)")+
  theme_classic()

fifth_graph <- ggplot(fifth,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est, show.legend= FALSE))+
  geom_point()+
  ggtitle("2030")+
  ylab("Biomass 1000 (MT)")+
  theme_classic()

all<-ggarrange(initial_graph, second_graph, third_graph, fourth_graph, fifth_graph, nrow=3, ncol=2, common.legend = TRUE, legend=FALSE)
all
ggsave("biomass_time.jpg", width=10, height=12, dpi=300)
```



Graphs seperated out by implmentation date (too similar to do all on one graph)
y axis= year; y-axis = biomass; size= catch, color = money made
F=Fmsy
** can see where the biomass equilibrium happenes

```{r}

library(dplyr)

fmsy<- read.csv(here::here("Scenarios", "PatchModel_FMSY.csv"))%>%
  filter(Adjusted=="IUU_0")


linepoint_fmsy<- fmsy%>%
  filter(Reserve_size == "5%" | Reserve_size== "BAU") %>%
  group_by(Year, Implementation_year, Adjusted) %>%
  summarize(Biomass_est=sum(Biomass_est), 
            Catch_est=sum(Catch_est), 
            PV_est=sum(PV_est)) %>%
    mutate(Biomass_est=Biomass_est/1000)

linepoint_fmsy$Implementation_year<- as.factor(circle_fmsy$Implementation_year)

#Genus_ts <- read_csv("data/Genus_ts.csv")

historic <- Genus_ts %>%
  filter(Adjusted == "IUU_0") %>%
  filter(year>="2005") %>%
  filter(year != "2015") %>%
  group_by(year) %>%
  summarize(catch=sum(catch),
            b=sum(b)) %>%
  mutate(b = b/1000)

colnames(historic) <- c("Year", "Catch_est", "Biomass_est")

initial <-linepoint_fmsy %>%
  filter(Implementation_year== "0") 
initial <- full_join(historic, initial, by=c("Year", "Biomass_est", "Catch_est"))

second <- filter(linepoint_fmsy, Implementation_year == "2015")
second <- full_join(historic, second, by=c("Year", "Biomass_est", "Catch_est"))

third <- filter(linepoint_fmsy, Implementation_year == "2020")
third <- full_join(historic, third, by=c("Year", "Biomass_est", "Catch_est"))

fourth <- filter(linepoint_fmsy, Implementation_year == "2025")
fourth <- full_join(historic, fourth, by=c("Year", "Biomass_est", "Catch_est"))

fifth <- filter(linepoint_fmsy, Implementation_year == "2030")
fifth <- full_join(historic, fifth, by=c("Year", "Biomass_est", "Catch_est"))

initial_graph <- ggplot(initial,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("BAU")

second_graph <- ggplot(second,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2015")

third_graph <- ggplot(third,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2020")

fourth_graph <- ggplot(fourth,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2025")

fifth_graph <- ggplot(fifth,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2030")

all<-ggarrange(initial_graph, second_graph, third_graph, fourth_graph, fifth_graph, nrow=3, ncol=2, common.legend = TRUE, legend="bottom")
all
#ggsave("biomass_time_fmsy.jpg", width=10, height=12, dpi=300)
```

Graphs seperated out by implmentation date (too similar to do all on one graph)
y axis= year; y-axis = biomass; size= catch, color = money made
OA and 40% protected


```{r}

library(dplyr)

linepoint <- res %>%
    filter(Reserve_size == "40%" | Reserve_size == "BAU") %>%
  group_by(Year, Implementation_year, Adjusted)%>%
  summarize(Biomass_est=sum(Biomass_est), 
            Catch_est=sum(Catch_est), 
            PV_est=sum(PV_est)) %>%
  mutate(Biomass_est=Biomass_est/1000)
linepoint$Implementation_year<- as.factor(linepoint$Implementation_year) 
  

#Genus_ts <- read_csv("data/Genus_ts.csv")

historic <- Genus_ts %>%
  filter(Adjusted == "IUU_0") %>%
  filter(year>="2005") %>%
  filter(year != "2015") %>%
  group_by(year) %>%
  summarize(catch=sum(catch),
            b=sum(b)) %>%
  mutate(b=b/1000)

colnames(historic) <- c("Year", "Catch_est", "Biomass_est")

initial <-linepoint %>%
  filter(Implementation_year== "0") 
initial <- full_join(historic, initial, by=c("Year", "Biomass_est", "Catch_est"))

second <- filter(linepoint, Implementation_year == "2015")
second <- full_join(historic, second, by=c("Year", "Biomass_est", "Catch_est"))

third <- filter(linepoint, Implementation_year == "2020")
third <- full_join(historic, third, by=c("Year", "Biomass_est", "Catch_est"))

fourth <- filter(linepoint, Implementation_year == "2025")
fourth <- full_join(historic, fourth, by=c("Year", "Biomass_est", "Catch_est"))

fifth <- filter(linepoint, Implementation_year == "2030")
fifth <- full_join(historic, fifth, by=c("Year", "Biomass_est", "Catch_est"))

initial_graph <- ggplot(initial,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("BAU") +
  ylab("Biomass 1000 (MT)")+
  theme_classic()

second_graph <- ggplot(second,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2015")+
  ylab("Biomass 1000 (MT)")+
  theme_classic()

third_graph <- ggplot(third,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2020")+
  ylab("Biomass 1000 (MT)")+
  theme_classic()

fourth_graph <- ggplot(fourth,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2025")+
  ylab("Biomass 1000 (MT)")+
  theme_classic()

fifth_graph <- ggplot(fifth,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2030")+
  ylab("Biomass 1000 (MT)")+
  theme_classic()

all<-ggarrange(initial_graph, second_graph, third_graph, fourth_graph, fifth_graph, nrow=3, ncol=2, common.legend = TRUE, legend="bottom")
all
ggsave("biomass_time_40protect.jpg", width=10, height=12, dpi=300)
```


Protect 20

```{r}

library(dplyr)

linepoint <- res %>%
    filter(Reserve_size == "20%" | Reserve_size == "BAU") %>%
  group_by(Year, Implementation_year, Adjusted)%>%
  summarize(Biomass_est=sum(Biomass_est), 
            Catch_est=sum(Catch_est), 
            PV_est=sum(PV_est))%>%
  mutate(Biomass_est=Biomass_est/1000)
linepoint$Implementation_year<- as.factor(linepoint$Implementation_year)
  

#Genus_ts <- read_csv("data/Genus_ts.csv")

historic <- Genus_ts %>%
  filter(Adjusted == "IUU_0") %>%
  filter(year>="2005") %>%
  filter(year != "2015") %>%
  group_by(year) %>%
  summarize(catch=sum(catch),
            b=sum(b))%>%
  mutate(b=b/1000)

colnames(historic) <- c("Year", "Catch_est", "Biomass_est")

initial <-linepoint %>%
  filter(Implementation_year== "0") 
initial <- full_join(historic, initial, by=c("Year", "Biomass_est", "Catch_est"))

second <- filter(linepoint, Implementation_year == "2015")
second <- full_join(historic, second, by=c("Year", "Biomass_est", "Catch_est"))

third <- filter(linepoint, Implementation_year == "2020")
third <- full_join(historic, third, by=c("Year", "Biomass_est", "Catch_est"))

fourth <- filter(linepoint, Implementation_year == "2025")
fourth <- full_join(historic, fourth, by=c("Year", "Biomass_est", "Catch_est"))

fifth <- filter(linepoint, Implementation_year == "2030")
fifth <- full_join(historic, fifth, by=c("Year", "Biomass_est", "Catch_est"))

initial_graph <- ggplot(initial,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("BAU") +
  ylab("Biomass 1000 (MT)")+
  theme_classic()

second_graph <- ggplot(second,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2015") +
  ylab("Biomass 1000 (MT)")+
  theme_classic()

third_graph <- ggplot(third,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2020") +
  ylab("Biomass 1000 (MT)")+
  theme_classic()

fourth_graph <- ggplot(fourth,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2025") +
  ylab("Biomass 1000 (MT)")+
  theme_classic()

fifth_graph <- ggplot(fifth,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2030")+
  ylab("Biomass 1000 (MT)")+
  theme_classic()

all<-ggarrange(initial_graph, second_graph, third_graph, fourth_graph, fifth_graph, nrow=3, ncol=2, common.legend = TRUE, legend="bottom")
all
ggsave("biomass_time_20protect.jpg", width=10, height=12, dpi=300)
```






Protect 30
```{r}

library(dplyr)

linepoint <- res %>%
    filter(Reserve_size == "30%" | Reserve_size == "BAU") %>%
  group_by(Year, Implementation_year, Adjusted)%>%
  summarize(Biomass_est=sum(Biomass_est), 
            Catch_est=sum(Catch_est), 
            PV_est=sum(PV_est))
linepoint$Implementation_year<- as.factor(linepoint$Implementation_year)
  

#Genus_ts <- read_csv("data/Genus_ts.csv")

historic <- Genus_ts %>%
  filter(Adjusted == "IUU_0") %>%
  filter(year>="2005") %>%
  filter(year < "2015") %>%
  group_by(year) %>%
  summarize(catch=sum(catch),
            b=sum(b))

colnames(historic) <- c("Year", "Catch_est", "Biomass_est")

initial <-linepoint %>%
  filter(Implementation_year== "0") 
initial <- full_join(historic, initial, by=c("Year", "Biomass_est", "Catch_est"))

second <- filter(linepoint, Implementation_year == "2015")
second <- full_join(historic, second, by=c("Year", "Biomass_est", "Catch_est"))

third <- filter(linepoint, Implementation_year == "2020")
third <- full_join(historic, third, by=c("Year", "Biomass_est", "Catch_est"))

fourth <- filter(linepoint, Implementation_year == "2025")
fourth <- full_join(historic, fourth, by=c("Year", "Biomass_est", "Catch_est"))

fifth <- filter(linepoint, Implementation_year == "2030")
fifth <- full_join(historic, fifth, by=c("Year", "Biomass_est", "Catch_est"))

initial_graph <- ggplot(initial,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("BAU")

second_graph <- ggplot(second,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2015")

third_graph <- ggplot(third,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2020")

fourth_graph <- ggplot(fourth,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2025")

fifth_graph <- ggplot(fifth,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2030")

all<-ggarrange(initial_graph, second_graph, third_graph, fourth_graph, fifth_graph, nrow=3, ncol=2, common.legend = TRUE, legend="bottom")
all
ggsave("biomass_time_30protect.jpg", width=10, height=12, dpi=300)
```







Juliette Notebook:
```{r}

linepoint <- res %>%
    filter(Reserve_size == "5%") %>%
  group_by(Year, Implementation_year, Adjusted)%>%
  summarize(Biomass_est=sum(Biomass_est), 
            Catch_est=sum(Catch_est), 
            PV_est=sum(PV_est))
linepoint$Implementation_year<- as.factor(linepoint$Implementation_year)
  
initial <-filter(linepoint, Implementation_year== "0")
second <- filter(linepoint, Implementation_year == "2015")
third <- filter(linepoint, Implementation_year == "2020")
fourth <- filter(linepoint, Implementation_year == "2025")
fifth <- filter(linepoint, Implementation_year == "2030")

linepoint_graph <- ggplot(initial,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  geom_point(data= second, aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point(data = third, aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point(data = fourth, aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point(data = fifth, aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))
  
linepoint_graph    
  
linepoint_graph_2 <- ggplot(linepoint,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point(data=linepoint[linepoint$Implementation_year =="0", ])+
  geom_point(data=linepoint[linepoint$Implementation_year =="2015", ])+
  geom_point(data=linepoint[linepoint$Implementation_year =="2020", ])+
  geom_point(data=linepoint[linepoint$Implementation_year =="2025", ])+
  geom_point(data=linepoint[linepoint$Implementation_year =="2030", ])

linepoint_graph_2



  
 
```
