---
title: "Report Pots"
author: "Seleni Cruz"
date: "February 13, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE, message=FALSE}
library(ggplot2)
library(here)
library(plotly)
library(tidyverse)
library(gganimate)
library(ggrepel)
library(ggridges)
library(ggpubr)
library(gridExtra)
library(grid)
library(jcolors)
```

#importing the dataset only looking at 2015-2050
```{r}
res<-read.csv(here::here("Priors_r_0.9","PatchModel_size_priors.csv"))%>%
  filter(Year <= 2065)

res$Implementation_year [res$Implementation_year== "0"] <- "BAU"
res$Implementation_year <- factor(res$Implementation_year, levels = c("Initial", "BAU", "2015", "2020", "2025", "2030"))
res$Reserve_size <- factor(res$Reserve_size, levels = c("BAU", "5%", "20%", "30%", "40%", "50%"))
  
bmsy<- expression(paste(B/B[MSY]))
fmsy <- expression(paste(F/F[MSY]))

```

1. Kobe of Initial Status 
```{r}
initial <- read.csv(here::here("Genus_pts.csv"))%>%
  filter(Adjusted=="IUU_0")

K_plot <- ggplot(initial, aes(x= bbmsy, y=ffmsy))+
  geom_rect(xmin = 0.0, xmax = 1.0, ymin = 0.0, ymax = 1, fill = 'yellow', alpha = 0.1) +
  geom_rect(xmin = 0, xmax = 1, ymin = 1.0, ymax = 7.1, fill = 'red', alpha = 0.1) +
  geom_rect(xmin = 1, xmax = 1.5, ymin = 0, ymax = 1, fill = 'green', alpha = 0.1) +
  geom_rect(xmin = 1, xmax = 2.1, ymin = 1, ymax = 7.1, fill = 'orange', alpha = 0.1)+
  geom_point(aes(size=catch), show.legend = FALSE)+
  scale_size(range = c(3, 10))+
  #geom_text_repel(aes(label = Name, size =10), direction="y", nudge_x=0.05, show.legend=FALSE)+
  labs(x=bmsy, y=fmsy)+
  geom_vline(xintercept = 1, linetype="dotted", color="black") +
  geom_hline(yintercept = 1, linetype="dotted", color="black") +
  scale_x_continuous(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0))+
  theme_classic(base_size = 10)

K_plot
#ggsave("KobeIntial_label.jpg", width=5, height=3, dpi=300)
ggsave("KobeIntial.jpg", width=5, height=3, dpi=300)
```


#2. Kobe plot in Open Access B/Bmsy 0.3 and various implementtion dates 

```{r}
initial <- read.csv(here::here("Genus_pts.csv"))%>%
  filter(Adjusted=="IUU_0")%>%
  mutate(Implementation_year = "Initial", Reserve_size = "BAU")%>%
  select(Name, Adjusted, Year, bbmsy, ffmsy, Implementation_year, Reserve_size)

OA_plot<-res%>%
  filter(Year== 2065 & Adjusted=="IUU_0")%>%
  filter(Reserve_size == "5%" | Reserve_size =="BAU")%>%
  select(Name, Adjusted, Year, bbmsy, ffmsy, Implementation_year, Reserve_size)%>%
  rbind(initial)

KobeOA <- ggplot(OA_plot, aes(x= bbmsy, y=ffmsy, group=Name))+
  geom_point(size=4, aes(color= Implementation_year, shape=Implementation_year))+
  scale_shape_manual(values=c(16, 17, 15, 18, 25, 20))+
  scale_colour_jcolors(palette = "pal8")+
  labs(x=bmsy, y=fmsy)+
  geom_vline(xintercept = 1, linetype="dotted", color="black") +
  geom_hline(yintercept = 1, linetype="dotted", color="black") +
  #scale_colour_discrete(name="Implementation year")+
  theme_classic(base_size = 10)

KobeOA
#ggsave("KobeOA.jpg", width=5, height=4, dpi=300)
```



```{r}
initial <- read.csv(here::here("Genus_pts.csv"))%>%
  mutate(Implementation_year = "Initial", Reserve_size = "BAU")%>%
  filter(!(Adjusted=="IUU_0"))%>%
  select(Name, Adjusted, Year, bbmsy, ffmsy, Implementation_year, Reserve_size)

OA_plot2 <-res%>%
  filter(Year== 2065 & Reserve_size == "5%")%>%
  filter(!(Adjusted=="IUU_0"))%>%
  select(Name, Adjusted, Year, bbmsy, ffmsy, Implementation_year, Reserve_size)%>%
  rbind(initial)

KobeOA <- ggplot(OA_plot2, aes(x= bbmsy, y=ffmsy, group=Name))+
  geom_point(size=3, aes(color= Implementation_year, shape=Implementation_year))+
  scale_shape_manual(values=c(16, 17, 15, 18, 25, 20))+
  scale_colour_jcolors(palette = "pal8")+
  labs(x=bmsy, y=fmsy)+
  geom_vline(xintercept = 1, linetype="dotted", color="black") +
  geom_hline(yintercept = 1, linetype="dotted", color="black") +
  #scale_colour_discrete(name="Implementation year")+
  theme_classic(base_size = 10)
KobeOA
KobeOA_inflated<- KobeOA+
   facet_wrap(~ Adjusted, ncol=2, labeller=label_parsed)
KobeOA_inflated
#ggsave("Kobe_inflated_0.05.jpg", width=8, height=6, dpi=300)

OA <-res%>%
  filter(Implementation_year=="2015", Year=="2065")

KobeOA_size<-ggplot(OA, aes(x= bbmsy, y=ffmsy, group=Name))+
  geom_point(size=2, aes(color=Name))+
  #scale_shape_manual(values=c(16, 17))+
  labs(title= "Fishery Status at various reserve network Sizes", x=bmsy, y=fmsy)+
  geom_vline(xintercept = 1, linetype="dotted", color="black") +
  geom_hline(yintercept = 1, linetype="dotted", color="black") +
  theme_classic(base_size = 18)

KobeOA_size
KobeOA_size<- KobeOA_size+
   facet_wrap(~ Reserve_size, ncol=2)
KobeOA_size
ggsave("Kobe_byMRSize.jpg", width=10, height=8, dpi=300)

```

#FMSY Kobe Plot

```{r}
ffmsy<- read.csv(here::here("Implementation_years", "PatchModel_FMSY.csv"))%>%
  filter(Adjusted=="MT" & Year == 2065)%>%
  filter(Total_Area=="5%")%>%
  rename(Implementation_year=Status, Size=Total_Area)

initial <- res%>%
  filter(Year == 2015 & Implementation_year == 0 & Adjusted=="MT")%>%
  mutate(Implementation_year = "initial")

plot<-ffmsy%>%
  rbind(initial)

FMSY<-ggplot(plot, aes(x= bbmsy, y=ffmsy, group=Implementation_year))+
  geom_point(size=3, aes(shape=Implementation_year, color=Implementation_year))+
  labs( x=bmsy, y=fmsy)+
  geom_vline(xintercept = 1, linetype="dotted", color="black") +
  geom_hline(yintercept = 1, linetype="dotted", color="black") +
  theme_classic(base_size = 16)
FMSY
ggsave("KobeFMSY.jpg", width=8, height=6, dpi=300)

```

#Kobe plot with implementation dates and different reserve sizes 
```{r}
plot2<-res%>%
  filter(Year== 2065, Adjusted== "IUU_0")

kobe2<- ggplot(plot2, aes(x= bbmsy, y=ffmsy))+
  geom_point(size=3, aes(color=Implementation_year, shape = Implementation_year))+
  #scale_shape_manual(values=c(16, 17, ))+
  labs(x=bmsy, y=fmsy)+
  geom_vline(xintercept = 1, linetype="dotted", color="black") +
  geom_hline(yintercept = 1, linetype="dotted", color="black") +
  theme_classic(base_size = 16)
kobe2<- kobe2 +
    facet_wrap(~ Reserve_size, ncol=2)
kobe2

ggsave("Kobe2.jpg", width=8, height=6, dpi=300)


kobe3<- ggplot(plot2, aes(x= bbmsy, y=ffmsy, group= Name))+
  geom_point(size=3, aes(color=Name, shape = Reserve_size))+
  #scale_shape_manual(values=c(16, 17, ))+
  labs(title= "Fishery Status with Reserve Implementation" , x=bmsy, y=fmsy)+
  geom_vline(xintercept = 1, linetype="dotted", color="black") +
  geom_hline(yintercept = 1, linetype="dotted", color="black") +
  theme_classic(base_size = 18)
kobe3<- kobe3 +
    facet_wrap(~ Implementation_year, ncol=2)
kobe3

#ggsave("Kobe3.jpg", width=10, height=12, dpi=300)


```

#Some fun line graphs 
```{r}
linedf<-res%>%
  group_by(Adjusted, Implementation_year, Reserve_size, Year)%>%
  summarize(Biomass_est=sum(Biomass_est)/1000, 
          Biomass_lo=sum(Biomass_lo)/1000, 
          Biomass_hi=sum(Biomass_hi)/1000,
          Catch_est=sum(Catch_est)/1000,
          Catch_lo=sum(Catch_lo)/1000, 
          Catch_hi=sum(Catch_hi)/1000, 
           PV_est=sum(PV_est)/1000000,
          PV_lo=sum(PV_lo)/1000000, 
          PV_hi=sum(PV_hi)/1000000)
#code for looking at when lines cross
#%>%
#  filter(Size== "BAU" | Size== "20%") %>%
#  filter(Implementation_year == "2015" | Implementation_year =="0") %>%
#  filter(Adjusted == "MT")

```


#Reserves at 5% of total area with different implemntation dates; I think this is what COBI wants to see 

```{r}
plot1<- linedf%>%
  filter(Adjusted == "IUU_0", Reserve_size=="5%")

B<-ggplot(plot1, aes(x=Year, y=Biomass_est, group=Implementation_year, color=Implementation_year))+
  geom_line(size=1.5)+
  labs(subtitle= "Biomass", y="1000s MT")+
  theme_classic(base_size = 24)

C<-ggplot(plot1, aes(x=Year, y=Catch_est, group=Implementation_year, color=Implementation_year))+
  geom_line(size=1.5)+
  labs(subtitle= "Catch", y="1000s MT")+
  theme_classic(base_size = 24)

P<-ggplot(plot1, aes(x=Year, y=PV_est, group=Implementation_year, color=Implementation_year))+
  geom_line(size=1.5)+
  labs(subtitle= "Profit", y= "MUSD")+
  theme_classic(base_size = 24)


Line1<-ggarrange(B, C, P, nrow=3, common.legend = TRUE, legend="bottom")
Line1
ggsave("Line1.jpg", width=6, height=8, dpi=300)
```


#Same plot with different reserve sizes 
```{r,  fig.height=10, fig.width=10}
plot2<- linedf%>%
  filter(Adjusted=="IUU_0")%>%
  filter (Implementation_year =="2015"|Implementation_year == "BAU")


B<-ggplot(plot2, aes(x=Year, y=Biomass_est, group=Reserve_size, color=Reserve_size))+
  geom_line(size=1.5)+
  labs(subtitle= "Biomass", y="1000s MT")+
  theme_classic(base_size = 12)

C<-ggplot(plot2, aes(x=Year, y=Catch_est, group=Reserve_size, color=Reserve_size))+
  geom_line(size=1.5)+
  labs(subtitle= "Catch", y="1000s MT")+
  theme_classic(base_size = 12)

P<-ggplot(plot2, aes(x=Year, y=PV_est, group=Reserve_size, color=Reserve_size))+
  geom_line(size=1.5)+
  labs(subtitle= "Profit", y= "MUSD")+
  theme_classic(base_size = 12)


Line2<-ggarrange(B, C, P, nrow=3, common.legend = TRUE, legend="bottom")
Line2

#ggplotly(Line2)
ggsave("Line2_priors.jpg", width=6, height=8, dpi=300)
```



